Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-03-15 src/tex/ms.tex
[showyourwork] overleaf sync

We use the scattering phase functions from \cite{treesstam2019} for an Earth-like planet with an ocean surface with patchy clouds and a wind-speed of $\SI{7}{\meter\per\second}$ at $\SI{670}{\nano\meter}$.
%
The $\SI{670}{\nano\meter}$ is close to the center of the Rc band for Vega ($\SI{642}{\nano\meter}$). 
%
We normalize the reflected light curve at the value of 90 degrees (quadrature) and multiply it with the contrast.
%
In addition, we map the orbital phase for circular orbits to the scattering phase angle and the on-sky separation given the inclinations of $60$ and $90$ degrees. \todo{Only the 60 degree plot is here at the moment}
%
Together they give the reflected light contrast as function of separation for a full orbit.
%
We multiply this flux with the degree of polarisation and retrieve the polarised contrast.
%
The resulting contrast curves are shown in \cref{fig:contrasts} for three of the closest target stars, the G~dwarf $\alpha$~Cen~A, the K~dwarf $\epsilon$~Eri and the M~dwarf Lalande~21185.

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/Contrast_vs_separation_inclination_angle_63.pdf}
   \caption{
    The reflected light contrast and orbital separation of an Earth-like planet with an ocean surface and patchy clouds over a planetary orbit assuming an orbital inclination of $60^\circ$ for the stars $\alpha$ Cen A, $\epsilon$ Eri and Lalande 21185. The solid line indicates the contrast in unpolarised light with the contrast at quadrature marked by a solid dot. The polarised component is indicated by the colored dots for which the color represents the scattering phase angle from quadrature. The light grey points show the quadrature contrasts of the other targets in the star list and the dashed lines indicate $1,2$ and $3$ times the \IWA\ for \hwo.
    }
    \label{fig:contrasts}
    \script{plot_contrasts.py}
\end{figure*}

>>>>

We use the scattering phase functions from \cite{treesstam2019} for an Earth-like planet with an ocean surface with patchy clouds and a wind-speed of $\SI{7}{\meter\per\second}$ at $\SI{670}{\nano\meter}$.
%
The $\SI{670}{\nano\meter}$ is close to the center of the Rc band for Vega ($\SI{642}{\nano\meter}$). 
%
We normalize the reflected light curve at the value of 90 degrees (quadrature) and multiply it with the contrast.
%
In addition, we map the orbital phase for circular orbits to the scattering phase angle and the on-sky separation given an inclination of $90$ degrees.
%
Together they give the reflected light contrast as function of separation for a full orbit.
%
We multiply this flux with the degree of polarisation and retrieve the polarised contrast.
%
The resulting contrast curves are shown in \cref{fig:contrasts} for three of the closest target stars, the G~dwarf $\alpha$~Cen~A, the K~dwarf $\epsilon$~Eri and the M~dwarf Lalande~21185.

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/Contrast_vs_separation_inclination_angle_90.pdf}
   \caption{
    The reflected light contrast and orbital separation of an Earth-like planet with an ocean surface and patchy clouds over a planetary orbit assuming an orbital inclination of $90^\circ$ for the stars $\alpha$ Cen A, $\epsilon$ Eri and Lalande 21185. The solid line indicates the contrast in unpolarised light with the contrast at quadrature marked by a solid dot. The polarised component is indicated by the colored dots for which the color represents the scattering phase angle from quadrature. The light grey points show the quadrature contrasts of the other targets in the star list and the dashed lines indicate $1,2$ and $3$ times the \IWA\ for \hwo.
    }
    \label{fig:contrasts}
    \script{plot_contrasts.py}
\end{figure*}
